InteroceptionStudy_GP

### 2022-12-03 Old scripts/IAPS_PREPROCESSING_GitSample.Rmd
test for Review
recover the power analyses files

---
title: "InteroceptionStudy_GPValidation"
Author: "Helio Cuve & "
date: "8 January 2021"
output: html_document
---

@@

# Preferences
list necessary package install them if not already and load them
```{r}
# devtools::install_github("dmirman/gazer")

@@

# setting a workspace
# change approproatelly

@@

Problem files
```{r}
# 355  - did not finish IAPS
# adjust below manually

  if (length(hdfFilesList) == 0){
    hdfFilesList

    return(message('No HDF5 files found in the directory provided.'))
  }
   f = 10
  for (f in 1:length(hdfFilesList)) {

unique(tmp.df$tNo)

Now cleaning gaze data and prepare data for ledalab and artifact

```{r, cleaning}
# function to read all the csvs into one dataframe

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/Step1_GpExtractor_Output/346-355")

# rm(tmp_full)
read_plus <- function(flnm) {
  data.table::fread(flnm, select = c("session_id","event_id", "time", "left_gaze_x", "left_gaze_y","right_gaze_x", "right_gaze_y","left_pupil_measure1",
                                     "right_pupil_measure1","gsr", "gsrv", 'hr', "hrv", "hrp", "status", "tNo",  "Condition", "screencontent", "stim", "ssid", "text")) %>% 
    mutate(filename = flnm)
}

# read all clean data 
tmp.df2 <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))

unique(tmp.df2$ssid)

table(is.na(tmp.df2$ssid))
# tmp.df2$ssid<- substr(tmp.df2$filename, 5,7)
head(tmp.df2)
# check we have all participants
# unique(tmp.df2$ssid)
tmp.df2<- subset(tmp.df2, !is.na(ssid))

#####################################################################################
# gp preprocessing funtion, checks for losses, averages gaze, pupil and pixelate
#####################################################################################

```{r, gppreprocessing}
gp_preprocessing = function(tmp.df2) {

  message(sprintf("step1 lft gaze validity"))

  # transform invalid gaze into NA based on validity codes

  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_x, NULL)
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '20', tmp.df2$left_gaze_y, NULL)
  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$left_gaze_y_cor, NULL)

  message(sprintf("step2 right gaze validity"))

  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '2', tmp.df2$right_gaze_x, NULL)
  #
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_x_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$status != '22', tmp.df2$right_gaze_y_cor, NULL)

  # pupil validity

  message(sprintf("step3 pupil validity"))
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '20', tmp.df2$left_pupil_measure1, NULL)
  tmp.df2$left_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$left_pupil_measure1, NULL)

  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '2', tmp.df2$right_pupil_measure1, NULL)
  tmp.df2$right_pupil_measure1<- if_else(tmp.df2$status != '22', tmp.df2$right_pupil_measure1, NULL)
  table(is.na(tmp.df2$right_pupil_measure1))

  # check gazepoint out of bounds nd repixelate (1920/2 = 960 by 1200/2 = 600. add half to normalised coordinates from psychopy)

  message(sprintf("step 4 cutting off screen in points and repixelate"))

  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)

  tmp.df2$left_gaze_y_cor<- if_else(tmp.df2$left_gaze_y_cor >= -600 & tmp.df2$left_gaze_y_cor <= 600, tmp.df2$left_gaze_y_cor, NULL)
  tmp.df2$right_gaze_y_cor<- if_else(tmp.df2$right_gaze_y_cor >= -600 & tmp.df2$right_gaze_y_cor <= 600, tmp.df2$right_gaze_y_cor, NULL)

  tmp.df2$left_gaze_x_cor_pix<- tmp.df2$left_gaze_x_cor+960
  tmp.df2$right_gaze_x_cor_pix<- tmp.df2$right_gaze_x_cor+960

  tmp.df2$left_gaze_y_cor_pix<- tmp.df2$left_gaze_y_cor+600
  tmp.df2$right_gaze_y_cor_pix<- tmp.df2$right_gaze_y_cor+600

  # is left or right an NA

  tmp.df2$left_na<- is.na(tmp.df2$left_gaze_x_cor) 
  tmp.df2$right_na<- is.na(tmp.df2$right_gaze_x_cor)
  tmp.df2$both_na<- if_else(tmp.df2$left_na == TRUE & tmp.df2$right_na == TRUE, TRUE, FALSE)

  message(sprintf("step5 gaze x  means"))

  tmp.df2$gaze_x_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_x_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_x_cor,
                                      ((tmp.df2$left_gaze_x_cor + tmp.df2$right_gaze_x_cor)/2)))
  message(sprintf("step6 gaze y means"))

  tmp.df2$gaze_y_cor<-if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_gaze_y_cor,
                              if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_gaze_y_cor,
                                      ((tmp.df2$left_gaze_y_cor + tmp.df2$right_gaze_y_cor)/2)))

  message(sprintf("step6 repixel gaze means"))

  tmp.df2$gaze_x_cor_pix<- tmp.df2$gaze_x_cor + 960
  min(tmp.df2$gaze_x_cor_pix, na.rm = TRUE)

  tmp.df2$gaze_y_cor_pix<- tmp.df2$gaze_y_cor+600
  min(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)

  # clean_pupil

  message(sprintf("cleaning pupil"))

  max(tmp.df2$left_pupil_measure1)

  tmp.df2$pupil<- if_else(tmp.df2$left_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$right_pupil_measure1,
                          if_else(tmp.df2$right_na == TRUE & tmp.df2$both_na == FALSE, tmp.df2$left_pupil_measure1,
                                  ((tmp.df2$left_pupil_measure1 + tmp.df2$right_pupil_measure1)/2)))

  # tmp.df2$trackloss<- if_else(tmp.df2$status > 0, TRUE, FALSE)
  tmp.df2$trialUnq<- paste(tmp.df2$tNo, paste(tmp.df2$screencontent, paste(tmp.df2$stim)))
  tmp.df2$distance = 630

  # min(tmp.df2$pupil, na.rm = TRUE)
  # max(tmp.df2$pupil, na.rm = TRUE)
  # colnames(tmp.df2)
  tmp.df2<- tmp.df2%>%
    arrange(time)
}

tmp.df2<- gp_preprocessing(tmp.df2)
 colnames(tmp.df2)

min(tmp.df2$pupil, na.rm = TRUE)
max(tmp.df2$gaze_y_cor_pix, na.rm = TRUE)

Compute proportions outside the screen

# check gazepoint out of bounds nd repixelate (1920/2 = 960 by 1200/2 = 600. add half to normalised coordinates from psychopy)

  x -960 by 960
  y -600 by 600

```{r eval=FALSE, include=FALSE}
range(tmp.df2$gaze_x_cor, na.rm = TRUE)

tmp.df2
range(tmp.df2$left_gaze_y, na.rm = TRUE)

range(tmp.df2$left_gaze_y, na.rm = TRUE)
range(tmp.df2$left_gaze_x, na.rm = TRUE)
tmp.df2$x_outside<- ifelse(tmp.df2$left_gaze_x < -960, TRUE,
                           ifelse(tmp.df2$left_gaze_x > 960, TRUE, FALSE))

tmp.df2$y_outside<- ifelse(tmp.df2$right_gaze_y < -600, TRUE,
                           ifelse(tmp.df2$right_gaze_y > 600, TRUE, FALSE))

table(tmp.df2$y_outside)
137/(185406+137)
0.0007383733*100

range(tmp.df, na.rm = TRUE)
tmp.df2$y_outside<-NULL

# rezeroing times by trial, by participants

```{r}
tmp.df3<- tmp.df2

# create start at every screen content
tmp.df3<- tmp.df3%>% 
  arrange(ssid, time, tNo)%>%
  group_by(ssid)%>%
  mutate(firststart = duplicated(trialUnq))

head(tmp.df3)

# make zero-times
tmp.df3$zero<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, NULL)

# fill in the zeros
tmp.df3<- tmp.df3%>%
  group_by(ssid, Condition, tNo)%>%
  # group_by(text)%>%
  fill(zero)

unique(tmp.df3$zero)

# rezero
tmp.df3<-tmp.df3%>%
  arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo)%>%
  mutate(timerezero = time - zero)

min(tmp.df3$timerezero, na.rm = TRUE)
max(tmp.df3$timerezero, na.rm = TRUE) # max shoudl be around 120s for 2 mnutes
natest<-subset(tmp.df3, is.na(tmp.df3$ssid) == TRUE)

# let's check to see if it looks fine
ggplot(subset(tmp.df3, tmp.df3$tNo == -1), aes(timerezero, gsr, colour = as.factor(ssid)))+
  geom_line()

# create a new time rezero where before stim start, time is negative

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition, screencontent)%>%
  mutate(firststartSTIM = duplicated(tNo))

#this will create a time in the stim start which we can use to do the a second rezeroing
tmp.df3$zero_stim<- if_else(tmp.df3$firststartSTIM == FALSE & tmp.df3$screencontent == 'stim', tmp.df3$time, NULL)

    # fill down
tmp.df3<- tmp.df3%>%
      arrange(time)%>%
      group_by(tNo, ssid)%>%
      fill(zero_stim, .direction = c('updown'))

   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim

   # check timerezero2
     range(tmp.df3$timerezero2, na.rm = TRUE)

# time 3 including rest
  # simply includes rest as is

tmp.df3$timerezero3<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$timerezero, tmp.df3$timerezero2)
min(tmp.df3$timerezero3, na.rm = TRUE)

# quick check that everything is fine

ggplot(subset(tmp.df3, tmp.df3$tNo == 27 ) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
    geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -7) , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

triggers

```{r}
unique(tmp.df3$tNo)

natest<- subset(tmp.df3, is.na(tmp.df3$tNo) == TRUE)
tmp.df3<- subset(tmp.df3, is.na(tmp.df3$tNo) == FALSE)

tmp.df3$intercept_time<- if_else(tmp.df3$firststart == FALSE, tmp.df3$time, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$time,
                                  NULL))

# takes a bit with a group - so don't run
# ggplot(tmp.df3, aes(time, gsr))+
#   geom_line()+
#   geom_vline(aes(xintercept = intercept_time))

unique(tmp.df3$tNo)

tmp.df3$trigger<- as.double(tmp.df3$tNo)

tmp.df3$trigger<- if_else(tmp.df3$firststart == FALSE, tmp.df3$trigger, 
                          if_else(tmp.df3$firststartSTIM == FALSE, tmp.df3$trigger, 0))
unique(tmp.df3$trigger)

tmp.df3$trigger <- if_else(tmp.df3$screencontent == 'fixation' &tmp.df3$firststart == FALSE, 100,
                          if_else(tmp.df3$screencontent == 'ValenceResp' & tmp.df3$firststart == FALSE, 101,
                             if_else(tmp.df3$screencontent == 'IntResp' & tmp.df3$firststart == FALSE, 102, tmp.df3$trigger)))

unique(tmp.df3$trigger)

tmp.df3$trigger<- if_else(tmp.df3$firststart == TRUE, 0, tmp.df3$trigger)

unique(tmp.df3$trigger)

writing for ledalab

```{r}

tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo,time)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

options(scipen = 999)

tmp.df3$gsr_ms <- 1/tmp.df3$gsr*100000
unique(tmp.df3$ssid)
max(tmp.df3$gsr_ms)
min(tmp.df3$gsr_ms)

# gsr for leda
colnames(tmp.df3)
db_GSR<- select(tmp.df3, c(3,  14, 17, 50, 49,51 ))
db_GSR$tNo<- NULL
colnames(db_GSR)

unique(db_GSR$Condition)

db_GSR$Condition2<- if_else(db_GSR$Condition == 'Rest', 'Rest', 'IAPS')
unique(db_GSR$Condition2)
db_GSR$split_column<- paste0(db_GSR$Condition2,paste(db_GSR$ssid))
unique(db_GSR$split_column)
  (sprintf("writing for ledlab"))

split_column<- unique(db_GSR$split_column)

split_gsr = split(db_GSR, list(db_GSR$split_column))

setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/PhysioLedalab/GP_gsr_forLeda/346-355_2021")

    for (ssid in names(split_gsr)) {
      write_tsv(split_gsr[[ssid]][,c("time","gsr_ms", "trigger")], paste0("gpgsr_", paste0(ssid),".txt"), col_names = FALSE)
    }

# baselining gsr
```{r}
# use ms to baseline
tmp.df3_backup<- tmp.df3

tmp.df3$gsr_bas<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, tmp.df3$gsr_ms, NULL)
# true if baseline within window
tmp.df3$gsr_bastrue<- if_else(tmp.df3$timerezero3 >= -3 & tmp.df3$timerezero3 < 0, TRUE, FALSE)

# create baseline median
tmp.df3$gsr_bas_mean<- NULL

tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)%>%
  group_by(ssid, tNo, gsr_bastrue)%>%
  mutate(gsr_bas_median = median(gsr_bas))

# fill the baseline mean
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median)

# fill up to complete
unique(tmp.df3$gsrv)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(gsr_bas_median, .direction = 'up')

# do baseline correction
# 
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  mutate(gsr_basCor = gsr_ms - gsr_bas_median)

# rest baselining
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, Condition)%>%
  mutate(gsr_restmedian = median(gsr_ms))

tmp.df3$gsr_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$gsr_ms- tmp.df3$gsr_restmedian, tmp.df3$gsr_basCor)

# plot diagnosis
ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

 ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= gsr_basCor, colour = as.factor(ssid)))+
  # stat_summary(geom = 'line', fun.data = 'mean')+
    geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2) 
  # tmp.df_norest$tNo<- as.factor(tmp.df_norest$tNo)

ggplot(subset(tmp.df3, tmp.df3$screencontent == 'stim') , aes(x = timerezero3, y= gsr_basCor, olour = as.factor(ssid)))+
    geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

tmp.df3_backup<- tmp.df3
# gsr respone
tmp.df3$gsr_resp_Log<- if_else(tmp.df3$timerezero3 > 1,TRUE, FALSE)
unique(tmp.df3$gsr_resp_Log)

tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log )%>%
    mutate(gsr_response =   max(gsr_basCor))

# gsr response for every bit
unique(tmp.df3$screencontent)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, screencontent)%>%
  mutate(gsr_response_scrcont =   max(gsr_basCor))

tmp.df3$gsr_response <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response)

tmp.df3<-
  tmp.df3%>%
  arrange(ssid, tNo,time)%>%
  group_by(ssid, tNo)%>%
    fill(gsr_response,  .direction = c('up'))

unique(tmp.df3$gsr_response )

tmp.df3_backup<- tmp.df3
```

#baseline and clean pupil

```{r}
library(gazer)

min(tmp.df3$pupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

tmp.df3$pupil<- if_else(tmp.df3$pupil> 7.2, tmp.df3$pupil, NULL)

tmp.df3$pupil<- if_else(tmp.df3$pupil< 45, tmp.df3$pupil, NULL)

tmp.df3_backup <- tmp.df3

# note that smothing and interpolating is order dependednt so order by ssid, trial and time
tmp.df3<- tmp.df3 %>%
  arrange(ssid, time,tNo)%>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=gazer::extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

min(tmp.df3$extendpupil, na.rm = TRUE)
max(tmp.df3$pupil, na.rm = TRUE)

# let's check

ggplot(subset(tmp.df3, tmp.df3$tNo == 3), aes(x = timerezero3, y= extendpupil , colour = as.factor(ssid)))+
      geom_line()
  # geom_line(aes(y = extendpupil), linetype = 'dashed', colour = 'red')

# Smooth and Interpolate
tmp.df3$subject<- tmp.df3$ssid
tmp.df3$trial = tmp.df3$trialUnq

# min(pup_extend$pupil, na.rm = TRUE)
tmp.df3$extendpupil
# ?smooth_interpolate_pupil

# library(gazer)

?smooth_interpolate_pupil

# vert order dependent
tmp.df3 <- gazer::smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

# tmp.df3<- tmp.df3 %>%
#   group_by(ssid, trialUnq,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=10, 
#                                     filter = 'moving',
#                                     type="linear", hz=20, n = 10)
# 
# 
# tmp.df3<-
#   tmp.df3%>%
#   arrange(ssid,tNo,time)
#   # group_by(ssid, tNo, timerezero3)%>%
# 
# tmp.df3te<- tmp.df3 %>%
#   group_by(ssid, Condition,tNo,screencontent) %>%
#   smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
#                                     extendblinks=TRUE, 
#                            step.first= 'smooth',
#                                     maxgap=Inf, 
#                                     filter = 'moving',
#                                     type="linear", hz=100, n = 5)

min(tmp.df3$pup_interp, na.rm = TRUE)
max(tmp.df3$pup_interp, na.rm = TRUE)

subset(tmp.df3, tNo == 20 & ssid == 347)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

subset(tmp.df3, tNo == -7 & ssid == 350)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()

subset(tmp.df3, tNo == 1)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   # geom_line(aes(y = extendpupil), color = 'red')+
  # geom_line(aes(y = pup_interp), colour = 'gray')+
    facet_grid(~ssid)
  # facet_grid(~Condition)
```

# create baseline pupil mean
```{r}
tmp.df3backup<- tmp.df3
tmp.df3$pup_bas<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, tmp.df3$pup_interp, NULL)
# true if bseline if baseline within widnown
tmp.df3$pup_bastrue<- if_else(tmp.df3$timerezero3 >= -1 & tmp.df3$timerezero3 < 1, TRUE, FALSE)

tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo, pup_bastrue)%>%
  mutate(pup_bas_med = median(pup_bas))

# fill the baseline mean pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid,tNo)%>%
  fill(pup_bas_med)

# fill up to complete pupil
tmp.df3<- tmp.df3%>%
  # arrange(time)%>%
  group_by(ssid, tNo)%>%
  fill(pup_bas_med, .direction = 'up')

# do baseline correction
tmp.df3<- tmp.df3%>%
  arrange(ssid, tNo, time)%>% # pay attentipn to order
  group_by(ssid, tNo)%>%
  mutate(pup_basCor = pup_interp - pup_bas_med)

# we only one the median for rest
tmp.df3<- tmp.df3%>%
  group_by(Condition)%>%
  mutate(pupilrest = median(pup_interp))

tmp.df3$pup_basCor<- if_else(tmp.df3$Condition == 'Rest', tmp.df3$pup_interp-tmp.df3$pupilrest, tmp.df3$pup_basCor)

# MAD removal
library(gazer)
max_pup<-tmp.df3 %>%
  dplyr::group_by(subject, trial) %>%
  dplyr::mutate(speed=speed_pupil(pup_interp,time)) %>%
  dplyr::mutate(MAD=calc_mad(speed))
  # dplyr::filter(speed < MAD)

tmp.df3<- max_pup

# instead of deleting, nus put NA
tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

tmp.df3$pup_interp_mad<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_interp, NULL)
# tmp.df3$pup_basCor<- if_else(tmp.df3$speed< tmp.df3$MAD, tmp.df3$pup_basCor, NULL)

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tNo == 10 & tmp.df3$ssid == 354) , aes(x = timerezero3, y= pup_basCor))+
    # geom_smooth(se = F)+
  geom_line()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
  xlim(-3,3)

# preparation
subset(tmp.df3, tNo == 10)%>%
  group_by(ssid, tNo)%>%
  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad, na.rm = TRUE))%>%
  ungroup()%>%
ggplot(aes(x = timerezero3, y= pupil_z))+
    # geom_smooth(se = F)+
  stat_summary(fun = mean, geom = 'line')+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
  xlim(-3,15)
```
unique(tmp.df3$ssid)

```{r}
# rest period
ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = T)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

```{r}
colnames(tmp.df3)
table(is.na(tmp.df3$gsr_ms))
table(is.na(tmp.df3$hr))

# heart rate

min(tmp.df3$hr, na.rm = TRUE)
max(tmp.df3$hr, na.rm = TRUE)

tmp.df3$hrv<- as.double(tmp.df3$hrv)
tmp.df3$hrv2<- if_else(is.na(tmp.df3$hrv) == TRUE, 999,tmp.df3$hrv)

tmp.df3$hr_clean<- tmp.df3$hr
tmp.df3$hr_clean<- as.double(tmp.df3$hr_clean)

tmp.df3$hr_clean<- if_else(tmp.df3$hrv2 >0,  tmp.df3$hr_clean, NULL)

tmp.df3$hr_clean<- if_else(tmp.df3$hr_clean > 40 & tmp.df3$hr_clean< 120, tmp.df3$hr_clean, NULL)

table(is.na(tmp.df3$hr_clean))
# interpolate, only 2 seconds 
library(zoo)

tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)

# tmp.df3$hr_interp =

tmp.df3<- tmp.df3%>%
  # arrange(ssid, time, tNo)%>%
  group_by(ssid, tNo,screencontent)%>%
  mutate(hr_interp = na.approx(hr_clean, na.rm=FALSE, maxgap =400))

  min(tmp.df3$hr, na.rm = TRUE)
ggplot(subset(tmp.df3, tmp.df3$tNo == -7 & tmp.df3$ssid == 352) , aes(x = timerezero3, y= hr_interp))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_clean), linetype = 'dashed', colour = 'green', size = 0.3)+
   geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)
    # geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    # geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    # geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

# na.approx(object, x = index(object), xout, ..., na.rm = TRUE, maxgap = Inf, along)
# z <- na.spline(zoo(y, x), maxgap = 2)

```{r}
tmp.df3 <- tmp.df3 %>%
    group_by(ssid, tNo, gsr_resp_Log, screencontent)%>%
    mutate(gsr_response_bycond =   max(gsr_basCor))

# tmp.df3$gsr_response_bycond <- if_else(tmp.df3$gsr_resp_Log == TRUE, tmp.df3$gsr_response, NULL)

colnames(tmp.df3)
# tmp.df4<- select(tmp.df3, c(1:3,10:22,27:30,33:37,44,46,47,51,53:56,60))

tmp.df4<- select(tmp.df3, c("session_id", "event_id", "ssid", "subject", "text", "trial","trialUnq", "tNo","trigger", "Condition" ,"screencontent","stim",
                            "time", "timerezero", "timerezero2", "timerezero3", "status","filename",
                            "left_gaze_x_cor_pix","right_gaze_x_cor_pix","left_gaze_y_cor_pix","right_gaze_y_cor_pix",  "gaze_x_cor_pix",  "gaze_y_cor_pix",
                            "pupil", "pup_interp_mad", "extendpupil","pup_basCor",
                            "hr", "hrv", "hrp", "hr_clean", 'hr_interp', 
                            'gsr_ms', 'gsr_basCor', 'gsr_response', 'gsr_response_bycond', 
                            "distance"))
head(tmp.df4)

# calculate trackloss
unique(tmp.df4$status)

tmp.df4$trackloss<- if_else(is.na(tmp.df4$gaze_x_cor_pix) == TRUE, 0, 
                         if_else(is.na(tmp.df4$gaze_y_cor_pix) == TRUE, 0, 1))
unique(tmp.df4$trackloss)

# tmp.df4$trackloss<- if_else(tmp.df4$status> 0, 1, 0)

tmp.df4$hr_trackloss<- if_else(is.na(tmp.df4$hr_clean) == TRUE, 0, 1) # 1 means valid, 0 missing

tmp.df4 <- tmp.df4 %>%
  group_by(ssid, tNo, trialUnq, text)%>%
  mutate(gaze_valid_prop = sum(trackloss)/n())%>%
  mutate(gaze_loss_prop = 1 - gaze_valid_prop)%>%
  mutate(hr_valid_prop = sum(hr_trackloss)/n())%>%
  mutate(hr_loss_prop = 1 - hr_valid_prop)

# check to see this is right
ggplot(subset(tmp.df4, tmp.df3$ssid == 353) , aes(x = tNo, y= hr_valid_prop))+
    # geom_smooth(se = F)+
  geom_line()+
  geom_line(aes(y = hr_loss_prop), linetype = 'dashed', colour = 'green', size = 0.3)
   # geom_line(aes(y = hr), linetype = 'dotted', colour = 'blue', size = 0.4)

>>>>

---
title: "InteroceptionStudy_GP"
Author: "Helio Cuve"
date: "8 January 2020"
output: html_document
---

@@

# Preferences
list necessary package install them if not already and load them
```{r}

@@

# setting a workspace

@@
